The Promise that R makes

### 2019-03-06 report/report.Rmd
Add analysis and fix corpus generation

---
title: "Laziness in R"
output:
  html_document:
    toc: true
    theme: united
params:
  summarized_data_dirpath: ../latest/analysis/summarized
  visualized_data_dirpath: ../latest/analysis/visualized
  image_format: png
editor_options:
  chunk_output_type: console
---

@@

```{r echo = FALSE, message = FALSE}

library(DT)
library(fs)
library(png)
library(stringr)
library(dplyr)
library(magrittr)
library(rlang)
library(knitr)
library(png)
library(grid)
library(gridExtra)
```

```{r datatsets, echo = FALSE}
import_data_table <- function(name) {
    promisedyntracer::read_data_table(path(params$summarized_data_dirpath, name))
}

show_table <- function(tablename) {
  datatable(import_data_table(str_c(tablename, "csv", sep = ".")),
            fillContainer = TRUE,
            filter = "top")
}

show_graph <- function(graphname) {
    include_graphics(path(params$visualized_data_dirpath, graphname))
}

show_graphs <- function(first_graphname, second_graphname) {
    load_graph <- function(graphname) {
        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
                                                graphname))),
                         interpolate = TRUE)
    }
    grid.arrange(load_graph(first_graphname),
                 load_graph(second_graphname),
                 ncol = 2)
}

count_labels <-
  Vectorize(function(x, digits = 2) {

@@

    if(is.na(x)) {
      "NA"
    } else if(x < 10^3) {
      paste0(x)
    } else if(x < 10^6) {
      paste_round(x, 1000, "K", sep=" ")
    } else if(x < 10^9) {
      paste_round(x, 10^6, "M", sep=" ")
    } else {
      paste_round(x, 10^9, "B", sep=" ")
    }
  },
  "x")
```
```{r echo = FALSE}
unique_closures <- 
    import_data_table("closures.csv") %>%
    group_by(function_id) %>%
    summarize(call_count = first(call_count),
              formal_parameter_count = first(formal_parameter_count)) %>%
    mutate(argument_count = call_count * formal_parameter_count)
```
This report summarizes the findings on the use of laziness in R.

Data from 15 packages and 26 vignettes.

* Number of functions: `r count_labels(length(unique_closures$function_id))`

* Number of calls: `r count_labels(sum(unique_closures$call_count))`

* Number of parameters: `r count_labels(sum(unique_closures$formal_parameter_count))`

* Number of arguments: `r count_labels(sum(unique_closures$argument_count))`

## Closures

### Closure Data
```{r echo = FALSE}
show_table("closures")
```

### Closure count by Call count

The following figure shows the distribution of the number of calls made to closures.

```{r echo = FALSE, out.width="1000px"}
show_graph("function_count_by_call_count.png")
```

```{r echo = FALSE}
show_table("function_count_by_call_count")
```

#### Observations

* Very few functions are called only once. We can remove these functions from the remaining analyses without affecting the representativity of our results.

* Majority of functions are called more than once.

### Closure count by Formal Parameter count

The following figure shows the distribution of the number of parameters of closures.

```{r echo = FALSE, out.width="1000px"}
show_graph("function_count_by_formal_parameter_count.png")
```

```{r echo = FALSE}
show_table("function_count_by_formal_parameter_count")
```

#### Observations
- Majority of functions have one, two or three parameters.
- A very small number of functions have zero parameters.

## Arguments

### Argument count by Argument Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_argument_mode.png")

```
```{r echo = FALSE}
show_table("argument_count_by_argument_mode")
```

### Argument count by Argument Use Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_argument_use_mode.png")
```

```{r echo = FALSE}
show_table("argument_count_by_argument_use_mode")
```

### Argument count by Argument Use Mode and Argument Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_argument_use_mode_and_argument_mode.png")
```

```{r echo = FALSE}
show_table("argument_count_by_argument_use_mode_and_argument_mode")
```

### Argument count by Argument Mode and Argument Use Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_argument_mode_and_argument_use_mode.png")
```

```{r echo = FALSE}
show_table("argument_count_by_argument_mode_and_argument_use_mode")
```

## Parameters

### Parameter count by Parameter Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_mode.png")
```
```{r echo = FALSE}
show_table("parameter_count_by_parameter_mode")
```

### Parameter count by Parameter Class

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_class.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_class")
```

### Parameter count by Parameter use Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_use_mode.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_use_mode")
```

### Parameter count by Parameter Class and Parameter Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_class_and_parameter_mode.png")
```
```{r echo = FALSE}
show_table("parameter_count_by_parameter_class_and_parameter_mode")
```

### Parameter count by Parameter Mode and Parameter Class

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_mode_and_parameter_class.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_mode_and_parameter_class")
```

### Parameter count by Parameter Class and Parameter Use Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_class_and_parameter_use_mode.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_class_and_parameter_use_mode")
```

### Parameter count by Parameter Use Mode and Parameter Class

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_use_mode_and_parameter_class.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_use_mode_and_parameter_class")
```

### Parameter count by Parameter Mode and Parameter Use Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_mode_and_parameter_use_mode.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_mode_and_parameter_use_mode")
```

### Parameter count by Parameter Use Mode and Parameter Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("parameter_count_by_parameter_use_mode_and_parameter_mode.png")
```

```{r echo = FALSE}
show_table("parameter_count_by_parameter_use_mode_and_parameter_mode")
```

## Arguments and Parameters

### Argument count by Parameter Class, Argument Mode and Argument Use Mode

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_parameter_class_and_argument_mode_and_argument_use_mode.png")
```

```{r echo = FALSE}
show_table("argument_count_by_parameter_class_and_argument_mode_and_argument_use_mode")
```

## Force Order

### Function count by Wrapper, Force Order Type and Force Order count

```{r echo = FALSE, out.width="1000px"}
show_graph("function_count_by_wrapper_force_order_type_and_force_order_count.png")
```

```{r echo = FALSE}
show_table("function_count_by_wrapper_force_order_type_and_force_order_count")
```

### Function count by Wrapper, Function Class, Force Order Type and Force Order count

```{r echo = FALSE, out.width="1000px"}
show_graph("wrapper_function_count_by_function_class_force_order_type_and_force_order_count.png")
```
```{r echo = FALSE, out.width="1000px"}
show_graph("nonwrapper_function_count_by_function_class_force_order_type_and_force_order_count.png")
```

```{r echo = FALSE}
show_table("function_count_by_wrapper_function_class_force_order_type_and_force_order_count")
```

>>>>

---
title: "The Promise that R makes"
output:
  html_document:
    toc: true
    theme: united
params:
  summarized_data_dirpath: ../latest/analysis/summarized
  visualized_data_dirpath: ../latest/analysis/visualized
  binary: FALSE
  compression_level: 0
  image_format: png
editor_options:
  chunk_output_type: console
---

@@

```{r echo = FALSE, message = FALSE}
library(DT)
library(fs)
library(png)
library(stringr)
library(dplyr)
library(magrittr)
library(rlang)
library(knitr)
library(png)
library(grid)
library(gridExtra)
library(promisedyntracer)
```

```{r datatsets, echo = FALSE, message = TRUE}
show_table <- function(tablename) {
    path(params$summarized_data_dirpath, tablename) %>%
    read_data_table(binary = params$binary, 
                    compression_level = params$compression_level) %>%
    datatable(fillContainer = TRUE, filter = "top")
}

show_graph <- function(graphname) {
    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
    include_graphics()
}

show_graphs <- function(first_graphname, second_graphname) {
    load_graph <- function(graphname) {
        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
                                                graphname, 
                                                ext = "png"))),
                         interpolate = TRUE)
    }
    grid.arrange(load_graph(first_graphname),
                 load_graph(second_graphname),
                 ncol = 2)
}
```
```{r utilities, echo = FALSE}
count_labels <-
    Vectorize(function(x, digits = 2) {

@@

      if(is.na(x)) {
        "NA"
      } else if(x < 10^3) {
        paste0(x)
      } else if(x < 10^6) {
        paste_round(x, 1000, "K", sep=" ")
      } else if(x < 10^9) {
        paste_round(x, 10^6, "M", sep=" ")
      } else {
        paste_round(x, 10^9, "B", sep=" ")
      }
    },
    "x")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("object_count_by_type")
```

```{r echo = FALSE}
show_table("object_count_by_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_call_count_by_type")
```

```{r echo = FALSE}
show_table("function_call_count_by_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_count_by_type")
```

```{r echo = FALSE}
show_table("function_count_by_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_call_count_by_method_type")
```

```{r echo = FALSE}
show_table("function_call_count_by_method_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_count_by_method_type")
```

```{r echo = FALSE}
show_table("function_count_by_method_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("closure_count_by_call_count")
```

```{r echo = FALSE}
show_table("closure_count_by_call_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("closure_count_by_formal_parameter_count")
```

```{r echo = FALSE}
show_table("closure_count_by_formal_parameter_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_call_count_by_return_value_type")
```

```{r echo = FALSE}
show_table("function_call_count_by_return_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("builtin_count_by_return_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("special_count_by_return_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("closure_count_by_return_value_type")
```

```{r echo = FALSE}
show_table("function_count_by_return_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("closure_count_by_wrapper_and_force_order")
```

```{r echo = FALSE}
show_table("closure_count_by_wrapper_and_force_order")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_call_count_by_type_and_jump")
```

```{r echo = FALSE}
show_table("function_call_count_by_type_and_jump")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("function_call_count_by_type_and_jump")
```

```{r echo = FALSE}
show_table("function_call_count_by_type_and_jump")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_distribution_by_category")
```

```{r echo = FALSE}
show_table("promise_distribution_by_category")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_distribution_by_type")
```

```{r echo = FALSE}
show_table("argument_distribution_by_type")
```

```{r echo = FALSE, out.width="1000px"}         
show_graph("argument_distribution_by_dot_dot_dot")
```

```{r echo = FALSE}         
show_table("argument_distribution_by_dot_dot_dot")
```

```{r echo = FALSE, out.width="1000px"}         
show_graph("argument_promise_distribution_by_nature")
```

```{r echo = FALSE}         
show_table("argument_promise_distribution_by_nature")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_distribution_by_sharing")
```

```{r echo = FALSE}
show_table("argument_promise_distribution_by_sharing")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_use_distribution_by_category")
```

```{r echo = FALSE}
show_table("promise_use_distribution_by_category")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_action_distribution_by_category")
```

```{r echo = FALSE}
show_table("promise_action_distribution_by_category")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_usage")
```

```{r echo = FALSE}
show_table("argument_count_by_usage")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("formal_parameter_count_by_usage")
```

```{r echo = FALSE}
show_table("formal_parameter_count_by_usage")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("formal_parameter_count_by_usage_class")
```

```{r echo = FALSE}
show_table("formal_parameter_count_by_usage_class")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("closure_count_distribution_by_usage_class")
```

```{r echo = FALSE}
show_table("closure_count_distribution_by_usage_class")
```
